#Prediction on Manners on how Exercises are Done  
##Data and package loading  
```{r}
library(caret)
library(rpart)
library(rpart.plot)
library(randomForest)
training <- read.csv("pml-training.csv")
testing <- testing <- read.csv("pml-testing.csv")
```

##Preprocessing and Explorary Data Analysis
```{r}
str(training,list.len =160)
```
  
There are 19622 records and 160 variables. However, there are many missing values for some of the variables at a glance. It is sensible to remove variables which has most of its values missing and the first 7 columns which are index, name of participants and timestamps.  
```{r}
indexToRemove <- which(colSums(is.na(training)|training=="")>0.9*dim(training)[1])
trainClean <- training[,-indexToRemove]
testClean <- testing[,-indexToRemove]
trainClean <- trainClean[,-c(1:7)]
testClean <- testClean[,-c(1:7)]
length(which(complete.cases(trainClean)))
```
  
It can be observed now that all 19622 rows of record has no more missing values.  

##Prepare Dataset for Prediction
```{r}
intrain <- createDataPartition(trainClean$classe, p=0.7, list=F)
trainSet <- trainClean[intrain,]
testSet <- trainClean[-intrain,]
rm(trainClean)
```
  
##Model Building  
###Decision Tree  
```{r cache=T}
set.seed(23333)
DTmodel<- train(classe~., trainSet,method = "rpart")
```
  
Prediction On Testset
```{r}
DTpred <- predict(DTmodel, testSet)
DT_ConMat <- confusionMatrix(testSet$classe,DTpred)
DT_ConMat$overall
```
The Accuracy is only 49.5% as shown.

##Random Forest
```{r cache=T}
RFmodel<- randomForest(classe~., trainSet)
RFpred <- predict(RFmodel, testSet)
RF_ConMat <- confusionMatrix(RFpred, testSet$classe)
RF_ConMat$overall
```
  
The accuracy is 99.5% which is very accurate.  

```{r}
plot(RFmodel)
```
  
From the graph, it can be seen that the error rate remains fairly constant from 100 to 500 trees. 

##Prediction on test dataset
Since random forest yield better accuracy, it is used to predict the "classe" of the test dataset
```{r}
final_pred <- predict(RFmodel,testClean)
final_pred
```

